\LARGE Micro- versus meso-scale population models for ecological forecasting under climate change

### 2014-12-04 manuscript/ms_MicroMeso.Rnw
figure update

<<echo=FALSE, include=FALSE, fig=TRUE, label=CoefFig, width=8.5, height=10, results=hide>>=
gQC <- read.csv("../montana/quadBM/vitalRateRegressions/growth/growthQuants.csv")
gQC <- gQC[129:144,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
gQC$X <- rep(coefNames, each=4)
gQC$rate <- "growth"
sQC <- read.csv("../montana/quadBM/vitalRateRegressions/survival/survivalQuants.csv")
sQC <- sQC[33:48,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
sQC$X <- rep(coefNames, each=4)
sQC$rate <- "survival"
rQC <- read.csv("../montana/quadBM/vitalRateRegressions/colonization/colonizationQuants.csv")
rQC <- rQC[29:44,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
rQC$X <- rep(coefNames, each=4)
rQC$rate <- "colonization"
plotQC <- rbind(gQC,sQC,rQC)
gQ <- ggplot(plotQC, aes(x=species, y=X50., color=rate))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.5, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5))+
  ylab("Standardized Coefficient Value")+
  xlab("Species")+
  facet_grid(X~.)+
  coord_flip()+
  theme_bw()+
  scale_color_manual(values=c("grey25", "steelblue", "slateblue"))+
  guides(color=guide_legend(title=""))+
  theme(legend.position="top")

gIC <- read.csv("../montana/ipm/vitalRateRegs/growth/growthQuants.csv")
gIC <- gIC[133:148,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
gIC$X <- rep(coefNames, each=4)
gIC$rate <- "growth"
sIC <- read.csv("../montana/ipm/vitalRateRegs/survival/survivalQuants.csv")
sIC <- sIC[133:148,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
sIC$X <- rep(coefNames, each=4)
sIC$rate <- "survival"
rIC <- read.csv("../montana/ipm/vitalRateRegs/recruitment/recruitmentQuants.csv")
rIC <- rIC[81:96,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
rIC$X <- rep(coefNames, each=4)
rIC$rate <- "colonization"
plotIC <- rbind(gIC,sIC,rIC)
gI <- ggplot(plotIC, aes(x=species, y=X50., color=rate))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.5, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5))+
  ylab("Standardized Coefficient Value")+
  xlab("Species")+
  facet_grid(X~.)+
  coord_flip()+
  theme_bw()+
  scale_color_manual(values=c("grey25", "steelblue", "slateblue"))+
#   guides(color=FALSE)+
  guides(color=guide_legend(title=""))+
  theme(legend.position="top")

@@

\begin{figure}[th!]
\begin{center}
\includegraphics[ width=\textwidth] {Fig-CoefFig}
\end{center}
\caption{Posterior means (points), 75\% credible intervals (heavy lines), and 95\% credible intervals (light lines) of climate effects in each vital rate statistical model. The quadrat level estimates are shown in left panels and individual level estimates are in right panels.}
\label{fig:CoefFig}
\end{figure}

>>>>

<<echo=FALSE, include=FALSE, fig=TRUE, label=CoefFig, width=8.5, height=10, results=hide>>=
gQC <- read.csv("../montana/quadBM/vitalRateRegressions/growth/growthQuants.csv")
gQC <- gQC[129:144,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
gQC$X <- rep(coefNames, each=4)
gQC$rate <- "growth"
sQC <- read.csv("../montana/quadBM/vitalRateRegressions/survival/survivalQuants.csv")
sQC <- sQC[33:48,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
sQC$X <- rep(coefNames, each=4)
sQC$rate <- "survival"
rQC <- read.csv("../montana/quadBM/vitalRateRegressions/colonization/colonizationQuants.csv")
rQC <- rQC[29:44,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
rQC$X <- rep(coefNames, each=4)
rQC$rate <- "colonization"
plotQC <- rbind(gQC,sQC,rQC)
gQ <- ggplot(plotQC, aes(x=species, y=X50., color=rate))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.25, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5), shape="|")+
  ylab("Standardized Coefficient Value")+
  xlab("Species")+
  facet_grid(X~.)+
  coord_flip()+
  theme_bw()+
  scale_color_manual(values=c("grey25", "steelblue", "slateblue"))+
  guides(color=guide_legend(title=""))+
  theme(legend.position="top")+
  ggtitle("Quadrat-level")

gIC <- read.csv("../montana/ipm/vitalRateRegs/growth/growthQuants.csv")
gIC <- gIC[133:148,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
gIC$X <- rep(coefNames, each=4)
gIC$rate <- "growth"
sIC <- read.csv("../montana/ipm/vitalRateRegs/survival/survivalQuants.csv")
sIC <- sIC[133:148,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
sIC$X <- rep(coefNames, each=4)
sIC$rate <- "survival"
rIC <- read.csv("../montana/ipm/vitalRateRegs/recruitment/recruitmentQuants.csv")
rIC <- rIC[81:96,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
rIC$X <- rep(coefNames, each=4)
rIC$rate <- "colonization"
plotIC <- rbind(gIC,sIC,rIC)
gI <- ggplot(plotIC, aes(x=species, y=X50., color=rate))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.25, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5), shape="|")+
  ylab("Standardized Coefficient Value")+
  xlab("Species")+
  facet_grid(X~.)+
  coord_flip()+
  theme_bw()+
  scale_color_manual(values=c("grey25", "steelblue", "slateblue"),
                     labels=c("recruitment", "growth", "survival"))+
#   guides(color=FALSE)+
  guides(color=guide_legend(title=""))+
  theme(legend.position="top")+
  ggtitle("Individual-level")

@@

\begin{figure}[th!]
\begin{center}
\includegraphics[ width=\textwidth] {Fig-CoefFig}
\end{center}
\caption{Posterior means (vertical ticks), 75\% credible intervals (heavy lines), and 95\% credible intervals (light lines) of climate effects in each vital rate statistical model. The quadrat level estimates are shown in left panels and individual level estimates are in right panels.}
\label{fig:CoefFig}
\end{figure}

### 2014-12-04 manuscript/ms_MicroMeso.tex
ms updates
added deviance and coefficient figures for climate effects
figure update

\begin{Schunk}
\begin{Soutput}
NULL
\end{Soutput}
\end{Schunk}

@@

\begin{figure}[th!]
\begin{center}
\includegraphics{Fig-CoefFig}
\end{center}
\caption{Posterior means (points), 75\% credible intervals (heavy lines), and 95\% credible intervals (light lines) of climate effects in each vital rate statistical model. The quadrat level estimates are shown in left panels and individual level estimates are in right panels. Color codes: blue = colonization/recruitment, green = growth, red = survival.}
\label{fig:CoefFig}
\end{figure}

>>>>

@@

\begin{figure}[th!]
\begin{center}
\includegraphics[ width=\textwidth] {Fig-CoefFig}
\end{center}
\caption{Posterior means (vertical ticks), 75\% credible intervals (heavy lines), and 95\% credible intervals (light lines) of climate effects in each vital rate statistical model. The quadrat level estimates are shown in left panels and individual level estimates are in right panels.}
\label{fig:CoefFig}
\end{figure}
